European or American? A re-examination of the transatlantic influence over the IMF

### 2025-08-13 manuscript/manuscript.qmd
remove "explanations in the literature"

While our baseline results indicate that European powers exert substantial influence over IMF lending outcomes, two common explanations in the literature could potentially account for these patterns without implying broad, institutionalised influence.

>>>>

While our baseline results indicate that European powers exert substantial influence over IMF lending outcomes, two plausible explanations could potentially account for these patterns without implying broad, institutionalised influence.
